Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-01 paper.qmd
Updated Figure 12

nldr_two_curvy_original <- umap_two_curvy_scaled |> 
  ggplot(aes(x = UMAP1, y = UMAP2)) + 
  geom_point(alpha=0.5, color = "#636363", size = 0.5) +
  xlim(c(-0.01, 1.1)) + ylim(c(-0.08, 0.57)) +
  interior_annotation("a", sc_ltr_pos)
```

@@

nldr_two_curvy_original + tsne_two_curvy_clust_plt +
  trimesh_two_curvy_removed1_with_data + trimesh_two_curvy_removed1_tsne_with_data +
  two_curvy_proj_umap_model +
  two_curvy_proj_tsne_model +
  two_curvy_proj_umap_all_model +
  two_curvy_proj_tsne_all_model +
  plot_layout(ncol = 2)
```

>>>>

nldr_two_curvy_original <- umap_two_curvy_scaled |> 
  ggplot(aes(x = UMAP1, y = UMAP2)) + 
  geom_point(alpha=0.5, color = "#636363", size = 0.5) +
  theme(aspect.ratio = 1) +
  #xlim(c(-0.01, 1.1)) + ylim(c(-0.08, 0.57)) +
  interior_annotation("a", sc_ltr_pos)
```

@@

nldr_two_curvy_original + tsne_two_curvy_clust_plt +
  trimesh_two_curvy_removed1 + trimesh_two_curvy_removed1_tsne_with_data +
  two_curvy_proj_umap_model +
  two_curvy_proj_tsne_model +
  two_curvy_proj_umap_all_model +
  two_curvy_proj_tsne_all_model +
  plot_layout(ncol = 2)
```
